Analytics Without Tuning Considered Harmful?

### 2015-08-12 tuningpredictor.tex
add a figure about Logistic Regression to refute that systematic literature review paper.

\subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,me07b}. In\cite{me07b}, naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets. In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically better than CART in terms of the AUC ranking. Such conclusions are not reliable since they can change when we elect to tune for different goals.

@@

In \tab{precisionbars} and \tab{fbars}, the tuned CART are better than or equal to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
terms of precision and F-measure, respectively. Results from the non-parametric Kolmogorov-Smirnov Test turn out that the performance 
scores of tuned CART and tuned Random Forests are not statistically different. This is the opposite of   
 Lessmann et al.~\cite{lessmann2008benchmarking}, the tuned Random Forest is not significantly better than tuned CART.
 In another result that is the reverse of \tab{precisionbars}, tuned WHERE is not necessarily
 any better than anything else.

 Therefore, it's not always safe to say ``LearnerX'' is the best or better than ``learnerY'' without pointing out the performance criteria or applying tuning techniques. That is, the answer to RQ2 is ``yes'' since tuning a set of learners
 changes the rankings of those learners regarding different criteria.

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
 \end{center}
\caption{Comparison between tuned and naive SVM learners with rbf and sigmoid kernels over the goal of F. }\label{fig:svm}
 \end{figure}

@@

 In \fig{features}, we show how tuning selects the optimal values for parameters. For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our supporting documents\footnote{\url{https://goo.gl/aHQKtU}}.
The default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$. Note that:
\bi
\item
The tunings learned by DE
were often very different to the default. That is, to achieve the performance improvements seen in the paper,
the default tuning parameters required a wide range of adjustments.
\item The tunings learned by DE were different in different data sets and for different goals.
\ei
Hence, we answer RQ6 as ``no'' since, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
sets are changed.Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
tuning is so easy and so fast (at least for defect predictors from static code attributes).

>>>>

\subsection{RQ2:  Does Tuning Change a Learner's Ranking ?}\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than 
another~\cite{lessmann2008benchmarking,me07b,hall2012systematic}. In\cite{me07b},
naive Bayes does better than C4.5 in terms of pd and balance over NASA MDP data sets.
In \cite{lessmann2008benchmarking}, Random Forest is considered to be statistically 
better than CART in terms of the AUC ranking. In the systematic literature review 
\cite{hall2012systematic}, authors claimed that defect predictors based on simple 
modeling techniques such as Logistic Regress perform well. Such conclusions are 
not stable across tuning process.

@@

In \tab{precisionbars} and \tab{fbars}, the tuned CART are better than or equal
to tuned Random Forests over $\frac{11}{17}$ and $\frac{10}{17}$ data sets in
terms of precision and F-measure, respectively. Results from the non-parametric
Kolmogorov-Smirnov Test turn out that the performance 
scores of tuned CART and tuned Random Forests are not statistically different.
This is the opposite of Lessmann et al.~\cite{lessmann2008benchmarking}, 
the tuned Random Forest is not significantly better than tuned CART.

\wei{added here!} In \fig{lr}, Logistic Regression performs better than untuned CART and Random
Forests over 17 data sets in terms of precision, which conforms with the statement
in \cite{hall2012systematic}: simple modeling techniques just perform well.
However, if we tuned CART and Random Forests, both of their performance was improved greatly. In some
data sets, CART and Random Forests are much better than Logistic Regression.

In another result that is the reverse of \tab{precisionbars}, tuned WHERE is not necessarily
 any better than anything else.

 Therefore, it's not always safe to say ``LearnerX'' is the best or better than ``learnerY'' 
 without applying tuning techniques. That is, the answer to RQ2 is ``yes'' since tuning a set of learners
 changes the rankings of those learners regarding different criteria.

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{LR_untuned.eps}\includegraphics[width=1.5in]{LR_tuned.eps}
 \end{center}
\caption{Comparison between Logistic Regression and CART as well as Random Forests before and after tuning. }\label{fig:lr}
 \end{figure}

@@

 In \fig{features}, we show how tuning selects the optimal values for parameters. For space limitation, only four parameters from WHERE learner are selected as representative and all the others can be found in our online support documents\footnote{\url{https://goo.gl/aHQKtU}}.
The default value for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$ as indicated in \tab{parameters}.  Note that:
\bi
\item
The tunings learned by DE
were often very different to the default. That is, to achieve the performance improvements seen in the paper,
the default tuning parameters required a wide range of adjustments.
\item The tunings learned by DE were different in different data sets and for different goals.
\ei
Hence, we answer RQ6 as ``no'' since, to achieve the improvements seen in this paper, tuning has to be repeated whenever the goals or data
sets are changed.Given this requirement to repeatedly run tuning, it is fortunate that (as shown above)
tuning is so easy and so fast (at least for defect predictors from static code attributes).
